Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-21 Docs/IJES/journal.tex
[A-15] In ESBMC-PS, how are the decision variables selected by each worker? Could two workers evaluate the same possible solution? Are the "fork" and "join" of the process employed a single time? Do the workers have communication or information interchange? Besides, the author/s said "the processor does not remain idle for a longer period and thus there is almost no optimization", then what is the contribution of this proposal?
minor changes

\vspace{2 mm}
\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

@@

The previous parallelization is implemented by continuously forking ESBMC instances in a sequential manner until the first violation is found. However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some period of time.

@@

\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. In addition, there is no communication among the workers, but each worker notifies the controller if a violation is found for its TipH value}.

>>>>

\vspace{2 mm}
\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be evaluated. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

@@

The previous parallelization is implemented by continuously forking ESBMC instances in a sequential manner until the first violation is found. However, since OpenMP only returns from a parallelized loop, when every forked thread finishes, some processing cores could remain idle for some time period.

@@

\textcolor{blue}{In contrast to ESBMC-SS, the second approach aims at removing the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. In addition, there is no communication among workers, but each worker notifies the controller if a violation is found for its TipH value}.
